Polynomial Time and Dependent Types

### 2023-07-11 paper/paper.tex
[ paper ] De-anonymised version

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  We combine dependent types with linear type systems that soundly and
  completely capture polynomial time computation. We explore two
  systems for capturing polynomial time: one system that disallows
  construction of iterable data, and one, based on the LFPL system of
  Martin Hofmann, that controls construction via a payment
  method. Both of these are extend to full dependent types via
  Quantitative Type Theory, allowing for arbitrary computation in
  types alongside guaranteed polynomial time computation in terms. We
  prove the soundness of the systems using a realisability technique
  due to Dal Lago and Hofmann.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  We combine dependent types with linear type systems that soundly and
  completely capture polynomial time computation. We explore two
  systems for capturing polynomial time: one system that disallows
  construction of iterable data, and one, based on the LFPL system of
  Martin Hofmann, that controls construction via a payment
  method. Both of these are extended to full dependent types via
  Quantitative Type Theory, allowing for arbitrary computation in
  types alongside guaranteed polynomial time computation in terms. We
  prove the soundness of the systems using a realisability technique
  due to Dal Lago and Hofmann.
